\providecommand{\submissionsection}[1]{\section*{#1}}

\submissionsection{Data and Code Availability}

\begin{sloppypar}
\ifdefined\blindreview
The simulator source, scenario configurations, validation scripts, generated tables and figures, supporting information files, committed report snapshots, and citation metadata are included in the anonymized review package. Public repository, release, and archive identifiers are withheld from the review-facing manuscript to preserve double-anonymized review and will be restored before any non-anonymous final publication. Report manifests record seed, run counts, runtime provenance, calibration checksum, and source Git commit for each generated report.

Private credentials and raw API payload archives are intentionally excluded from version control; normalized public-data snapshots and source-status manifests are committed under \texttt{data/snapshots/}. The Makefile exposes tests, report generation, validation, calibration queues, paper builds, submission packaging, and archive-handoff checksum generation. Its claim-audit path includes \texttt{claim-boundary-audit}, \texttt{claim-source-dependency-audit}, and \texttt{claim-posture-audit}. The Wiley-oriented package is generated with \texttt{make submission-package}, and the double-anonymized review package is generated with \texttt{make blinded-review-package}. The pinned environmental validation snapshot is generated with \texttt{make snapshot-2024-env}.
\else
The simulator source, scenario configurations, validation scripts, generated tables and figures, supporting information files, committed report snapshots, and citation metadata are publicly maintained at \url{https://github.com/Jacoba1100254352/lobby-capture-simulator}. The code is released under the MIT License, and this review bundle is associated with \href{https://github.com/Jacoba1100254352/lobby-capture-simulator/releases/tag/paper-publication-readiness-2026-06-19-r207}{release r207}. Report manifests record seed, run counts, runtime provenance, calibration checksum, and source Git commit for each generated report.

Private credentials and raw API payload archives are intentionally excluded from version control; normalized public-data snapshots and source-status manifests are committed under \texttt{data/snapshots/}. The Makefile exposes tests, report generation, validation, calibration queues, paper builds, submission packaging, and archive-handoff checksum generation. Its claim-audit path includes \texttt{claim-boundary-audit}, \texttt{claim-source-dependency-audit}, and \texttt{claim-posture-audit}. The Wiley-oriented package is generated with \texttt{make submission-package}. The pinned environmental validation snapshot is generated with \texttt{make snapshot-2024-env}.
\fi
\end{sloppypar}

\submissionsection{AI Use Disclosure}

OpenAI ChatGPT/Codex was used as an assistant for code scaffolding, editorial revision, research-prompt drafting, and manuscript organization. The author reviewed and edited the output and is responsible for all text, code, citations, analyses, and conclusions. AI tools were not used to fabricate, alter, or manipulate empirical source data or simulation results.

\submissionsection{Funding}

No external funding is reported.

\submissionsection{Conflict of Interest}

The author declares no conflicts of interest.
