\section{Purpose of the Supporting Information}

This supplement records implementation details that should not carry the main article's narrative burden. It makes the model schedule, scenario catalog, validation artifacts, source-panel boundaries, source-capability status, dark-money bridge limits, intermediary bridge limits, revolving-door bridge limits, procurement-denominator limits, procurement-modification composition limits, procurement-benchmark crosswalk, causal-calibration target audit, first-wave causal protocols, first-wave source readiness, and procurement-refresh readiness easy to inspect.

\section{Model Schedule and State}

Each simulation tick selects one policy contest and resolves it through the active institutional arena. The state update order is fixed:

\begin{enumerate}
  \item Select a contest from the scenario contest mix using the seeded random source.
  \item Replenish lobby budgets through client funding when expected private gain, exposure, secrecy needs, or reform threat justify additional money.
  \item Evaluate substitution pressure for each lobby organization and choose a channel strategy.
  \item Allocate finite spending across direct access, agenda access, information distortion, public campaigns, litigation threats, campaign finance, dark money, revolving-door routes, intermediaries, and defensive reform spending.
  \item Apply channel effects to public support, public benefit, private gain, dark-money influence, campaign finance pressure, litigation threat, revolving-door influence, comment-record distortion, procurement pressure, and hidden influence.
  \item Generate influence-network paths from funders and lobby organizations through channels, intermediaries, venues, and targets.
  \item Triage rulemaking comments into unique information, organized technical content, duplicate templates, and synthetic or low-authenticity comments.
  \item Resolve the contest in its arena under the reform regime, public backlash, hidden substitution pressure, and stochastic noise.
  \item Apply detection and sanctions.
  \item Update lobby strategy memory, issue-specific funding multipliers, regulator queue pressure, watchdog focus, adaptation speed, and reform-decay pressure.
\end{enumerate}

The repository copy of the ODD-style description is maintained in \texttt{docs/odd-model.md} and is included with the submission bundle as supporting information.

\section{ODD Summary}

\textbf{Purpose.} The model is designed to stress-test anti-capture reforms when organized interests can substitute across influence channels, messengers, venues, and financing routes. It is a mechanism model for diagnostic comparison, not an estimated policy-effect model.

\textbf{Entities and state variables.} Lobby organizations hold budgets, channel skills, issue preferences, reform-threat sensitivity, evasion skill, strategy memory, and defensive spending rules. Clients and funders hold exposure, private-gain, secrecy, and public-financing attributes. Institutional actors are represented through officials, regulators, candidates, watchdogs, enforcement agencies, reform regimes, arenas, and policy contests. Contests store arena type, issue domain, capture risk, public benefit, private gain, technical complexity, procurement exposure, comment docket structure, and reform status.

\textbf{Scheduling.} A run is a sequence of contest ticks. Each tick samples a contest, replenishes funding, evaluates substitution pressure, allocates spending, updates influence-network paths and rulemaking-comment records, resolves the institutional arena, applies enforcement, and updates strategy memory and institutional pressure indices.

\textbf{Inputs and initialization.} Scenarios combine a reform regime, initial influence strategy, evasion profile, contest mix, and calibration profile. The default build uses committed normalized source snapshots and fixtures; live API refreshes are separate from the review bundle.

\textbf{Submodels.} The main submodels are client funding, channel allocation, substitution switching, comment triage, influence-network construction, arena resolution, enforcement, strategy adaptation, source-moment extraction, validation diagnostics, and portfolio scoring.

\textbf{Stochasticity.} Randomness enters through contest sampling, channel-allocation variation, process detection, sanctions, and final contest resolution. Reported campaign, sensitivity, ablation, interaction, portfolio, and mechanism-comparison runs use fixed seeds and multi-run summaries.

\textbf{Outputs.} Reports separate observed capture, hidden influence, hidden capture, total influence distortion, substitution risk, defensive spending, administrative burden, channel shares, source-panel diagnostics, and multi-seed standard deviations.

\section{Scenario Families}

The scenario catalog is organized around mechanism families rather than institutional venues alone. The families are:

\begin{itemize}
  \item baseline and disclosed lobbying;
  \item low-salience technical rulemaking;
  \item campaign-finance, dark-money, and outside-spending pressure;
  \item revolving-door and advisory substitution;
  \item think-tank, association, and sponsored-expert intermediaries;
  \item procurement and vendor venue-shifting;
  \item hard lobbying budgets and shadow-lobbying stress;
  \item public financing, democracy vouchers, public-interest representation funds, and public advocate offices;
  \item real-time disclosure, machine-readable meeting logs, beneficial-owner disclosure, comment-authenticity systems, cooling-off enforcement, randomized audits, sanctions, procurement firewalls, and venue-shifting detection;
  \item reform bundles, ablations, interactions, sensitivity sweeps, and portfolio screens.
\end{itemize}

The generated scenario catalog in \texttt{docs/scenario-catalog.md} remains the authoritative scenario reference.

\section{Full Campaign Scenario Table}

\input{tables/full_campaign_appendix.tex}

\section{Primary Evaluation Rule}

The primary reform criterion is total influence distortion. A reform is treated as a distortion failure when observed capture falls by at least 0.02 and total modeled distortion rises by at least 0.02. It is treated as a substitution warning when observed capture falls but one or more hidden diagnostics rises:

\begin{align*}
\Delta observedCapture &< 0,\\
\Delta hiddenInfluence &> 0 \quad \text{or}\\
\Delta hiddenCapture &> 0 \quad \text{or}\\
\Delta totalDistortion &> 0 \quad \text{or}\\
\Delta substitutionRisk &> 0.
\end{align*}

If visible lobbying spend falls while hidden diagnostics or channel movement worsen, but observed capture does not fall, the row is labeled as a visible-channel warning rather than a distortion failure. General worsening rows are kept separate. This diagnostic is implemented in \texttt{scripts/validate-reports.py}. The generated outputs are \texttt{reports/substitution-audit.csv}, \texttt{reports/substitution-audit.md}, plus the apparent-failure table, substitution-warning table, and warning map in the main manuscript.

\section{Composite Diagnostic Weights}

The main article's composite-weight table lists the implemented weights for total influence distortion and design loss. Total influence distortion is a clamped additive diagnostic over contest outcomes, hidden-channel diagnostics, information distortion, procurement pressure, comment flooding, opacity, venue shifting, and administrative burden. Because some inputs are correlated, generated CSVs also report grouped raw components: observed/capture pressure, hidden substitution, information/procurement, network/venue, process burden, and the raw pre-clamp component sum. Design loss is used only for the portfolio screen and weights total distortion, hidden capture, substitution risk, administrative burden, opacity, legitimate-advocacy chill, and speech-restriction risk while rewarding cross-venue detection and participation protection.

Switch-rule diagnostics are reported as scenario-level averages in Table~\ref{tab:switch-rule-diagnostics}. The baseline column is the behavioral score used by the model. The equal-weight, anonymity-heavy, and enforcement-cost-heavy columns recompute the switch score from the same normalized terms without changing the realized run, so reviewers can inspect whether high substitution pressure is being driven by a single weighting convention.

\input{tables/switch_rule_snapshot.tex}

Composite-diagnostic variants are reported for selected portfolio rows in Table~\ref{tab:diagnostic-variant-snapshot}. The equal-weight distortion diagnostic averages observed capture, hidden capture, policy distortion, procurement bias, comment flooding, technical distortion, opacity, venue-shift load, and administrative burden. The hidden-discounted diagnostic halves the hidden-substitution component before clamping. The burden-heavy design loss puts additional weight on administrative burden and legitimate-advocacy chill.

\input{tables/diagnostic_variant_snapshot.tex}

\section{Generated Report Artifacts}

The reproducible report pipeline writes:

\begin{itemize}
  \item campaign, mechanism-comparison, sensitivity, ablation, interaction, and portfolio CSV and Markdown reports;
  \item source moments from normalized public-data panels;
  \item source-panel inventory diagnostics;
  \item source-capability audit separating implemented routes from snapshot support;
  \item dark-money bridge audit separating opaque-capacity proxies from adjacent outside-spending, electoral-communication, and 527 rows;
  \item intermediary bridge audit separating local campaign-intermediary, nonprofit-capacity, IRS 527, and Form 990 routing rows;
  \item revolving-door bridge audit separating LDA covered-position proxies from documented post-employment personnel-movement rows;
  \item procurement-denominator audit separating action-history rows from award-level bridge rows;
  \item procurement-modification composition audit decomposing action-level modification rows by source route, agency, award type, and recipient concentration;
  \item procurement-benchmark crosswalk remapping top-contractor concentration and ex-post modification ranges to the observed USAspending denominators;
  \item procurement-refresh readiness report documenting SAM/FPDS acquisition modes, quota handling, USAspending bulk-transaction strata fallback behavior, and the remaining calibrated-claim boundary;
  \item causal-calibration target audit naming the independent evidence classes required before calibrated policy-simulation claims can clear;
  \item first-wave causal protocol report translating the shortest empirical upgrade path into units, shocks, comparison designs, linkage keys, and falsification checks;
  \item first-wave source-readiness audit mapping those protocols to committed source products, bounded/proxy support, missing products, and blocking issues;
  \item validation summary, classified calibration queue, and calibration-readiness audit;
  \item substitution audit with distortion-failure, warning, and channel-shift tradeoff labels;
  \item LaTeX log audit checking final manuscript, Wiley, and supplement logs for unresolved citation, reference, fatal error, or rerun-required states;
  \item generated paper tables, figures, local PDF, Wiley PDF, supplement PDF, and Wiley submission archive;
  \item submission-readiness audit synthesizing claim posture, empirical-bridge scope, policy-language, layout, visual, and reproducibility gates;
  \item post-package Regulation \& Governance guideline-readiness audit checking journal target metadata, word limit, title-page metadata, declarations, figures, tables, supporting information, and LaTeX package contents while leaving the live author-page refresh as a manual final-submission control.
\end{itemize}

The Wiley submission archive includes a package-member checksum manifest alongside its supporting-information files and generated report bundle. The artifact checker compares packaged report files against the repository copies and validates the package manifest against ZIP member bytes so the reviewer bundle cannot silently omit or stale-copy a generated report.

The separate archive-handoff manifest is generated after the Wiley archive is built. It records the DOI-deposit asset set and stable source-metadata checksums. Local release-machine checksums for the rendered PDFs and submission ZIP are written under \texttt{dist/release-asset-checksums.*}; those ignored files are intended for release-upload or DOI-deposit verification and are kept outside the Wiley ZIP.

The canonical local check is:

\begin{verbatim}
make paper-artifacts-check
\end{verbatim}

\section{Validation Layers}

Validation proceeds in four layers. Parser and fixture tests enforce source schemas before normalized source rows enter calibration. The source-moments target extracts direct and proxy distributional moments for lobbying, campaign finance, electioneering and communication-cost rows, rulemaking, procurement, intermediaries, public financing, and revolving-door panels. The report-validation target compares model outputs against broad benchmark ranges and the parameter map, scopes high-end dark-money/Super PAC routing to explicit opaque electoral-routing stress cases, scopes candidate public-financing uptake to clean candidate-adoption scenarios, scopes regulator backlog to referral/workload-bearing rows, scopes duplicate-compression benchmarks to comment-authentication and related deduplication-tooling scenarios, and marks \texttt{source\_gap} rows when a source panel is too narrow or proxy-backed to test the benchmark directly. The substitution audit distinguishes clean improvements, distortion failures, and substitution warnings. Channel movement without higher hidden influence or distortion is treated as a tradeoff rather than a failure.

The portfolio target ranks candidate reform bundles by total distortion, hidden capture, substitution risk, administrative burden, network opacity, legitimate-advocacy chill, speech-restriction risk, cross-venue detection, and participation protection. The calibration-queue target classifies misses into model tuning, metric splits, direct source moments, scenario coverage, scale alignment, and benchmark review. Future snapshots can add health, transportation, SAM/FPDS crosswalk panels for procurement modification coding and exclusions, DIME, LobbyView, all-organization Form 990 routing rows, broader IRS 527 slices, FACA and witness records, federal, state, and additional local public-financing rows, broader nonprofit-routing and donor-identity source exports, lobbyist-bundling records, and richer revolving-door source exports once the environmental slice is stable.

\section{Source-Panel Coverage}

The 2024 EPA/ENV snapshot is a reproducibility scaffold, not a representative empirical panel. It is strongest for LDA, OpenFEC Schedule E, OpenFEC electioneering and communication-cost rows, NYC CFB public-financing and intermediary rows, Seattle Democracy Voucher rows, Regulations.gov, Federal Register, source-native IRS Form 8872 rows for a bounded 527 alphabetic slice, bounded ProPublica/IRS Schedule I nonprofit-routing rows for top dark-money-capacity EINs, USAspending schema checks, the multi-agency USAspending top-award procurement bridge, the no-agency-filtered national-volume USAspending transaction/action panel, the expanded stratified 12-agency quarterly USAspending transaction/action panel, the archived USAspending bulk transaction summary, the procurement benchmark crosswalk, and LDA-derived covered-position revolving-door rows. Procurement source moments separate the selected concentration denominator, award-level competition, and transaction/action modification diagnostics; when the bulk summary is present, it supplies the preferred public transaction-history denominator while the top-award bridge remains a separate high-value diagnostic. Modification diagnostics are reported as transaction-row, distinct-award, and amount-weighted shares so source users can see whether a high modification signal is row-driven, award-driven, or volume-driven. The procurement-denominator audit in \texttt{reports/procurement-denominator-audit.md} records which rows support national concentration diagnostics, which rows are action-history denominators, and which rows are award-level bridges. The procurement-modification composition audit in \texttt{reports/procurement-modification-composition-audit.md} decomposes the action panel by source route, agency, award type, recipient concentration, and distinct-award coverage so high modified-action shares are not mistaken for a SAM/FPDS-calibrated rate. The procurement-benchmark crosswalk in \texttt{reports/procurement-benchmark-crosswalk.md} remaps the old top-contractor range as a high-concentration slice diagnostic rather than a configured-agency aggregate benchmark, and remaps the old ex-post modification range as a delta or stress-screen concept rather than an absolute transaction-incidence benchmark. The procurement-refresh readiness report in \texttt{reports/procurement-refresh-readiness.md} records the no-network SAM/FPDS acquisition plan, extract-mode and offset-strata paths, quota handling, fallback policy, the archived USAspending bulk denominator, and the claim boundary that keeps calibrated policy-simulation claims outside the present manuscript until causal calibration and SAM/FPDS-style modification coding are reconciled; a separate ignored \texttt{make sam-contract-awards-preflight} target performs a one-row redacted quota/access probe before live runs. The dark-money bridge audit in \texttt{reports/dark-money-bridge-audit.md} records that the committed dark-money bridge separates IRS EO BMF opaque-capacity proxies from 80 public ProPublica/IRS Schedule I nonprofit-routing transfer rows, Super PAC, electioneering, communication-cost, IRS 527, and local campaign-intermediary rows; the Schedule I rows are not donor-identity evidence. The intermediary bridge audit in \texttt{reports/intermediary-bridge-audit.md} records that the committed bridge has local campaign-intermediary rows, IRS EO BMF capacity proxies, and bounded IRS 527 rows, but no representative Form 990 nonprofit-routing network beyond the Schedule I rows carried in the dark-money bridge. The revolving-door bridge audit in \texttt{reports/revolving-door-bridge-audit.md} records that the committed revolving-door bridge is an LDA covered-position proxy and separates it from documented post-employment personnel-movement rows. The codebase has an optional SAM.gov Contract Awards importer for the procurement action schema with synchronous offset page-index strata through \texttt{SAM\_CONTRACT\_AWARDS\_OFFSET\_STARTS} and asynchronous JSON/CSV extract downloads through \texttt{SAM\_CONTRACT\_AWARDS\_EXTRACT\_MODE}; this path is now most useful for exclusions, offer counts, protest/firewall overlays, and crosswalking USAspending modification coding. Public financing and dark-money bridge rows are separate panels. This prevents public-financing program rows or dark-money exports from being mistaken for ordinary FEC receipts, and it keeps Schedule I nonprofit-routing rows separate from super PAC, electioneering, communication-cost, 527, capacity-proxy, and other adjacent outside-spending rows. The source bridge remains incomplete for hidden-donor identity evidence, representative national public-financing program data, SAM/FPDS procurement coding crosswalks, representative all-organization Form 990 nonprofit routing beyond the top-EIN Schedule I slice, complete IRS 527 coverage beyond the bounded alphabetic slice, and documented post-employment movement beyond LDA-derived covered-position records.

The source-panel inventory in \texttt{reports/source-panel-inventory.md} is included in the submission bundle. The source-capability audit in \texttt{reports/source-capability-audit.md} separates implemented live-source routes from the evidence actually present in the frozen snapshot; an implemented importer does not strengthen a manuscript claim unless the committed snapshot contains usable rows and the claim ledger permits that claim. These reports should be read before using any model output as more than a mechanism diagnostic.

\section{Claim Boundary Audit}

The claim-boundary audit in \texttt{reports/claim-boundary-audit.md} is generated from the source-panel inventory and included in the submission bundle. It records, for each source panel, the support-level label, permitted claim boundary, claim to avoid, and next evidence needed before stronger empirical language would be justified. This is the repository-level guardrail for separating empirical source support from synthetic mechanism results.

The claim-source dependency audit in \texttt{reports/claim-source-dependency.md} maps manuscript claim families to the source panels and source moments they depend on. Table~\ref{tab:claim-source-dependency} highlights bounded or not-cleared claim families, while the generated CSV and Markdown reports retain the cleared rows as well.

\input{tables/claim_source_dependency.tex}

The causal-calibration target audit in \texttt{reports/causal-calibration-targets.md} names the independent causal estimands, required evidence designs, current source support, clearance criteria, and first-wave upgrade path that must be satisfied before the project can claim calibrated reform effects or representative national hidden-channel magnitudes. It covers hidden donor routing, substitution elasticity, procurement modification capture, revolving-door access, public financing, comment authenticity and uptake, enforcement deterrence, meeting disclosure, intermediary networks, and venue-shifting detection.

The first-wave causal protocol report in \texttt{reports/first-wave-causal-protocols.md} operationalizes the shortest empirical upgrade path into units of analysis, treatment or shock definitions, comparison designs, linkage keys, minimum source products, falsification checks, sensitivity checks, and claim-upgrade boundaries. Table~\ref{tab:first-wave-causal-protocols} summarizes those protocols; the generated Markdown and CSV reports retain the full linkage and threat-model details.

\input{tables/first_wave_causal_protocols.tex}

The first-wave source-readiness audit in \texttt{reports/first-wave-source-readiness.md} is the corresponding pre-estimation source gate. It records which committed source products support each protocol, which support is only bounded or proxy evidence, and which source products still block causal estimation. In the present bundle, no first-wave protocol is marked ready to estimate calibrated effects.

The claim-posture audit in \texttt{reports/claim-posture-audit.md} summarizes the same evidence at the manuscript level. It clears the mechanism-model article posture, bounds the empirical bridge, and keeps calibrated policy-simulation claims outside the present manuscript scope until the causal-calibration target audit and source panels justify that stronger claim.

The policy-claim language audit in \texttt{reports/policy-claim-language-audit.md} mechanically scans the manuscript, supplement, generated-table sources, and paper-facing documentation for calibrated-policy, causal-effect, policy-ranking, and representativeness language. The audit flags any such phrase that does not appear with local claim-boundary language, providing a reproducible check against accidental scope and policy-effect overclaims.

The LaTeX log audit in \texttt{reports/latex-log-audit.md} checks the final local manuscript, Wiley manuscript, and supplement logs for unresolved citations, references, fatal LaTeX errors, and rerun-required states. Overfull and underfull boxes remain visible in that report for human visual review, but unresolved compile state blocks the paper artifact gate.

The submission-readiness audit in \texttt{reports/submission-readiness.md} summarizes the review package posture. Its expected state for this manuscript is \texttt{ready\_for\_mechanism\_review}: the bundle is suitable for mechanism-model review with a bounded empirical bridge, while calibrated policy-effect claims remain blocked.

The repository release includes a Regulation \& Governance guideline-readiness audit at \path{reports/reggov-guidelines-readiness.md}. It records the locally verifiable journal and Wiley submission checks, is generated after the Wiley ZIP, and is not copied into that ZIP. Its expected state is \texttt{ready\_with\_manual\_live\_check}: committed files and the generated Wiley package satisfy local checks, while the live journal author page remains a final manual refresh.

\section{Decision Rules and Parameters}

The implementation exposes mechanism-facing parameters rather than estimated coefficients. The most important rules are:

\begin{itemize}
  \item Client funding increases with issue preference, exposure, private gain, calibration issue scale, secrecy incentives, and reform-threat pressure. Public-match and voucher sources lower large-donor dependence; dark-money sources increase opacity and legal-risk exposure.
  \item Donor concentration in reports now blends the simulated contribution ledger with source-derived top-donor concentration, Herfindahl concentration, and large-donor shares from the campaign-finance bridge. This avoids treating a report-level donor-Gini proxy as the only donor-network anchor.
  \item Procurement bridge risk now separates initial awards from post-award modifications and uses recipient concentration, single-bid or limited-competition indicators, modification share, price-only awards, protest flags, exclusion flags, and firewall coverage.
  \item Substitution activates when visible-channel pressure, anonymity value, messenger credibility, intermediary fit, venue overlap, and evasion freedom exceed legal cost, disclosure cost, cross-venue detection, and setup time. The threshold is deliberately low enough for stress scenarios to reveal channel migration.
  \item A distortion failure requires more than channel movement. The audit flags a row as a failure when observed capture falls while total distortion rises, as a substitution warning when hidden influence, hidden capture, or substitution risk rises after observed capture falls, and as a visible-channel warning when visible lobbying falls while hidden diagnostics worsen.
\end{itemize}

The source-facing parameters and benchmark ranges are maintained in \path{data/calibration/parameter-map.csv}. The reporting-error benchmark maps to \texttt{reportingErrorDetectionRate}, a narrow disclosure-and-audit diagnostic, while \texttt{detectionRate} remains the broader modeled capture-detection rate. The campaign-sanction benchmark maps to \texttt{campaignSanctionIncidence}, while \texttt{sanctionRate} remains the broader per-contest capture-sanction event rate. Report-level bounded diagnostics remain synthetic unless the validation summary classifies the target as a source moment.

\section{Figure and Layout Audit}

Paper figures are generated as SVGs and converted to Wiley-preferred PDF graphics. The script \texttt{scripts/generate-interaction-figures.py} uses simple label-placement logic with visible callout lines so point labels remain distinct and connected to the corresponding point. The script \texttt{scripts/audit-paper-layout.py} checks the generated PDFs for sparse float pages, excessive vertical whitespace, and figure or table pages with too little surrounding readable text. Its report is written to \texttt{reports/paper-layout-audit.md}. A separate visual checklist is written to \texttt{reports/manual-visual-audit.md}; it checks generated SVG label boxes for overlap, bounds, and leader-line coverage where callout labels exist and records table-float layout status.

\section{Calibration Priorities}

The model remains a mechanism article until the following source panels and causal-design loops improve. The generated causal-calibration target audit should control priority order: first-wave rows are the shortest source-to-manuscript path for strengthening the empirical bridge, while second-wave rows broaden representativeness and mechanism coverage.

\begin{itemize}
  \item hidden-donor identity evidence and representative nonprofit or intermediary routing panels beyond the top-EIN Schedule I slice;
  \item representative national public-financing and voucher participation records beyond the local NYC and Seattle program rows;
  \item SAM/FPDS procurement crosswalks covering modification coding, offer counts, exclusions, protests, and firewalls;
  \item richer revolving-door and advisory-access records;
  \item comment-authenticity and duplicate-compression panels linked to agency response text, plus enforcement-event panels that measure audit, referral, sanction, and backlog effects;
  \item scenario-specific causal designs for high-end outside spending, opaque electoral routing, broader shadow-lobbying substitution, cooling-off evasion, and cross-venue detection;
  \item public-financing uptake and regulator-workload panels that support causal comparisons rather than only benchmark-scope plausibility checks.
\end{itemize}

The calibration queue in \texttt{reports/calibration-queue.md} records classified validation-summary cleanup rows. It is separate from the causal-calibration target audit, which remains the controlling worklist for calibrated policy-simulation claims.

\section{How to Read the Bundle}

The supporting files are organized to make the boundary between model assumptions and evidence visible. The source moments and source-panel inventory should be read first when assessing empirical scope. They state which panels are direct or proxy-backed, which are usable within scope, and whether any panels are thin, fixture-supported, or missing. The mechanism-comparison report should be read next because it shows the consequence of enabling substitution relative to simpler model modes. The campaign, sensitivity, ablation, interaction, and portfolio reports are then best interpreted as stress tests under those model assumptions. The submission-readiness and Regulation \& Governance guideline-readiness audits should be read last because they summarize which claim posture and local journal-format checks the complete bundle supports, while separating final journal-submission requirements such as DOI archiving, human scholarly signoff, and live author-page refresh. The manual read-through checklist in \texttt{reports/final-human-readthrough.md} is included for final submission control, but it remains pending until signed for the current release tag.

Replication uses \texttt{make paper-artifacts-check}, which regenerates reports, tables, figures, PDFs, layout and visual audits, and the submission ZIP from checked-in sources. Live-source refreshes are separate so exploratory API output cannot silently alter the review bundle.
