\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{url}

\title{Lobby Capture Simulator: Modeling Strategic Influence, Regulatory Capture, and Anti-Capture Reform}
\author{Jacob Anderson}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
This paper introduces the Lobby Capture Simulator, a Java-based agent simulation focused on lobbying, money in politics, regulatory capture, and anti-capture reform. Unlike a legislature-centered institutional simulator where lobbying is one modifier on votes, this model treats organized interests as the central strategic actors. Lobby organizations allocate finite budgets across direct access, agenda access, information distortion, public campaigns, litigation threats, campaign finance, dark money, revolving-door access, and defensive spending against reform. The first runnable slice tests whether meaningful anti-capture reform threats cause organized interests to shift from ordinary policy capture into defensive reform blocking, and whether bundled reforms remain effective after that adaptation.
\end{abstract}

\section{Motivation}

Lobbying and regulatory capture are not merely legislative pressure terms. Organized interests can shape outcomes through campaign finance, public-information distortion, technical comments, litigation delay, procurement design, enforcement priorities, and post-government employment incentives. A useful simulation must therefore model lobbying as an influence economy rather than as a scalar attached to a bill.

The project is intended for comparative institutional analysis. The first priority is to make assumptions explicit enough that reform bundles can be stress-tested against adaptation and evasion. Empirical data are used as plausibility constraints for spending, disclosure, campaign finance, rulemaking, and procurement distributions, not as causal identification by themselves.

\section{Model Overview}

The current implementation contains lobby organizations, public officials, regulators, candidates, enforcement agencies, reform regimes, policy contests, influence arenas, and scenario reports. A policy contest may represent a statute, agency rule, enforcement priority, procurement decision, litigation posture, election pressure point, or anti-capture reform.

Each tick follows six steps:

\begin{enumerate}
  \item A policy contest is selected from the scenario's contest mix.
  \item Lobby organizations choose a strategy and allocate finite budgets.
  \item Influence channels modify public support, public benefit, private gain, information distortion, dark-money influence, revolving-door influence, campaign finance influence, and litigation threat.
  \item The relevant arena resolves the contest under the active reform regime.
  \item Enforcement may detect and sanction capture attempts.
  \item Lobby organizations update strategy memory and issue-specific spending multipliers.
\end{enumerate}

\section{Actors and Channels}

Lobby organizations carry issue preferences, budget accounts, influence intensity, access capital, technical expertise, public campaign skill, information bias, astroturf skill, litigation skill, revolving-door network strength, disclosure avoidance skill, reform-threat sensitivity, and defensive multipliers. Current channels are direct access, agenda access, information distortion, public campaign, litigation threat, campaign finance, dark money, revolving door, and defensive reform spending.

Reform regimes include disclosure, real-time contact transparency, beneficial-owner disclosure, contact logs, lobbying bans, cooling-off rules, public financing, democracy vouchers, contribution limits, dark-money disclosure, public advocates, blind review, anti-astroturf controls, enforcement budgets, audits, sanctions, appeal delay, defensive-spending caps, administrative cost, false-positive cost, and constitutional challenge risk.

\section{Strategic Allocation}

The model treats lobbying as a budget allocation problem under institutional constraints. Clients first replenish lobby organizations when expected private gain, exposure, and secrecy needs justify additional spending. For client \(c\), lobby \(l\), issue domain \(d\), and contest \(t\), funding is stylized as

\[
F_{c,l,t} =
\operatorname{clip}\left(k P_{l,d} E_{c,t} S_d (0.35 + G_{c,d} + R_{l,t}), 0, F_{\max}\right),
\]

where \(P_{l,d}\) is lobby issue preference, \(E_{c,t}\) is regulatory, procurement, enforcement, or campaign exposure, \(S_d\) is the calibration issue scale, \(G_{c,d}\) is client private gain, and \(R_{l,t}\) is reform-threat funding pressure for anti-capture contests. Funding enters the lobby budget and is also recorded as a money flow with source type, disclosure lag, traceability, legal risk, reputational risk, and contest linkage.

Lobby organizations then allocate channel spending from their available accounts. Each channel weight combines the active strategy, issue preference, expected return memory, and evasion incentives:

\[
A_{l,j,t} =
\min \left(B_{l,j,t}, I_l P_{l,d} W_{s,j}(1 + M_{l,j})(1 + Q_{j,t})\right),
\]

where \(B_{l,j,t}\) is spendable channel budget, \(I_l\) is influence intensity, \(W_{s,j}\) is the strategy weight for channel \(j\), \(M_{l,j}\) is learned return memory, and \(Q_{j,t}\) is an evasion or reform-threat adjustment. Channel allocations update public support, agenda access, information distortion, campaign influence, dark-money influence, litigation threat, revolving-door influence, and defensive anti-reform pressure.

Rulemaking contests carry a docket. Comment campaigns are generated from public-campaign, dark-money, and information-distortion spending. Anti-astroturf strength raises authentication and reduces synthetic comments; sponsor expertise and information bias affect technical-claim credibility. The arena then resolves the contest using the resulting docket authenticity, template saturation, and information distortion.

Enforcement applies after contest resolution. Detection probability increases with audit rate, enforcement budget, sanctions, public visibility, and evasion legal risk. When detected, sanctions reduce capture effects and add an evasion penalty. This makes evasion valuable only when opacity gains exceed the expected enforcement and disclosure costs.

\section{First Campaign Snapshot}

Table~\ref{tab:first-campaign} reports selected results from the current campaign snapshot: 40 runs per scenario, 80 contests per run, seed 42. The full snapshot is generated by \texttt{make campaign} and written under the \texttt{reports/} directory.

\begin{table}[h]
\centering
\scriptsize
\begin{tabular}{@{}lrrrrr@{}}
\toprule
Scenario & Capture & Reform & Defensive & Dark money & Funding \\
\midrule
Open access lobbying & 0.6094 & 0.5171 & 0.4689 & 0.1094 & 0.0722 \\
Reform threat mobilization & 0.0428 & 0.9363 & 0.6430 & 0.2105 & 0.1351 \\
Full anti-capture bundle & 0.0000 & 1.0000 & 0.5934 & 0.1740 & 0.1214 \\
Bundle with evasion & 0.0000 & 1.0000 & 0.5974 & 0.2488 & 0.1648 \\
Low-salience rulemaking & 0.8744 & 0.0000 & 0.0000 & 0.1200 & 0.0682 \\
\bottomrule
\end{tabular}
\caption{Current simulation snapshot. Metrics are comparative model outputs, not calibrated empirical estimates.}
\label{tab:first-campaign}
\end{table}

The early result is directionally useful: reform threats trigger substantial defensive spending, and evasion scenarios shift toward dark money. Low-salience technical rulemaking remains the weakest surface in the first implementation, which is consistent with the model's emphasis on information asymmetry and weak public attention.

\section{Sensitivity Snapshot}

The current sensitivity sweep varies enforcement, disclosure, public financing, cooling-off, and evasion freedom around the full anti-capture bundle. Table~\ref{tab:sensitivity} reports selected rows from \texttt{make sensitivity}: 30 runs per scenario, 70 contests per run, seed 142.

\begin{table}[h]
\centering
\small
\begin{tabular}{@{}lrrrr@{}}
\toprule
Scenario & Directional & Reform success & Dark-money share & Evasion shift \\
\midrule
Public financing 1.25 & 0.7759 & 1.0000 & 0.1702 & 0.2424 \\
Public financing 0.35 & 0.7213 & 1.0000 & 0.1722 & 0.2457 \\
Evasion 0.00 & 0.7686 & 1.0000 & 0.1165 & 0.0000 \\
Evasion 0.60 & 0.7683 & 1.0000 & 0.2484 & 0.8538 \\
Enforcement 0.35 & 0.7679 & 0.9974 & 0.1697 & 0.2505 \\
Disclosure 0.35 & 0.7683 & 0.9900 & 0.1259 & 0.0000 \\
\bottomrule
\end{tabular}
\caption{Selected sensitivity sweep rows. The current bundle is robust in this stylized setup, but evasion freedom strongly shifts spending into opaque channels.}
\label{tab:sensitivity}
\end{table}

\section{Ablation Snapshot}

Ablation reporting removes one reform component from the full anti-capture bundle under a deliberately stressed contest mix. Table~\ref{tab:ablation} reports the current \texttt{make ablation} snapshot: 40 runs per scenario, 80 contests per run, seed 242. The baseline full bundle has a capture rate of 0.0000 in this stress test, so the capture increase column is equal to the observed capture rate after removal.

\begin{table}[h]
\centering
\scriptsize
\begin{tabular}{@{}lrrrrr@{}}
\toprule
Removed component & Capture increase & Reform & Dark money & Comment distortion & Donor Gini \\
\midrule
Public advocate/blind review & 0.0378 & 0.9825 & 0.1766 & 0.0001 & 0.1450 \\
Enforcement & 0.0178 & 0.9955 & 0.1823 & 0.0001 & 0.1624 \\
Public financing/vouchers & 0.0006 & 0.9978 & 0.1760 & 0.0001 & 0.1432 \\
Beneficial-owner disclosure & 0.0000 & 1.0000 & 0.2457 & 0.0001 & 0.1485 \\
Cooling-off rules & 0.0000 & 1.0000 & 0.1750 & 0.0001 & 0.1463 \\
Anti-astroturf authentication & 0.0000 & 1.0000 & 0.1783 & 0.0003 & 0.1454 \\
\bottomrule
\end{tabular}
\caption{Selected ablation results. Removing public advocate/blind-review capacity creates the largest modeled capture opening, while removing beneficial-owner disclosure mainly shifts spending toward dark money.}
\label{tab:ablation}
\end{table}

\section{Empirical Bridge}

The implementation separates empirical distributional anchors from causal mechanisms. Normalized LDA fixture rows constrain issue funding scale and disclosure lag. Normalized FEC rows constrain donor concentration, public-financing share, and traceability. Normalized Federal Register and Regulations.gov fixture rows constrain docket size, comment authenticity, template saturation, and technical-claim credibility.

Those inputs do not estimate the causal effect of a disclosure rule, voucher system, or cooling-off ban. They provide plausible ranges for the simulation state variables. The default fetch workflow copies deterministic fixtures into \texttt{data/raw/}; optional \texttt{--live} modes normalize caller-provided CSV paths or URLs into the same schemas. The causal structure remains explicit in the model equations and arena rules, so validation should compare simulated distributions and directional responses against external data before treating any scenario ranking as substantively reliable.

\section{Validation Plan}

Validation will proceed in layers. LDA data constrain lobbying budgets, clients, registrants, and issue distributions. FEC data constrain campaign finance concentration and outside-spending pressure. Federal Register and Regulations.gov data constrain rulemaking timing, docket volume, comment volume, and agency/topic mix. Voteview and govinfo bill status data constrain legislative arena baselines. Seattle democracy voucher and New York City public matching-funds data constrain public-financing scenarios. USAspending data constrain procurement exposure and recipient concentration \cite{ldaData,fecData,federalRegisterApi,regulationsGovApi,voteview,seattleVouchers,usaspending}.

\section{Next Work}

The next model increment should replace generic live CSV hooks with source-native LDA, FEC, Federal Register, and Regulations.gov downloaders. The next behavioral increment should let clients, regulators, and watchdogs adapt over longer horizons. The next paper increment should generate LaTeX tables from stable CSV snapshots instead of copying values by hand.

\bibliographystyle{plain}
\bibliography{references}

\end{document}
