\documentclass[11pt]{article}

\PassOptionsToPackage{hyphens}{url}
\usepackage[margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{url}

\title{Strategic Channel Substitution in Regulatory Capture: An Agent-Based Model of Anti-Capture Reform}
\author{Jacob Anderson\\Independent Researcher\\United States\\\texttt{jacobdanderson@gmail.com}}
\date{June 15, 2026}
\hypersetup{
  pdftitle={Title Page for Strategic Channel Substitution in Regulatory Capture},
  pdfauthor={Jacob Anderson},
  pdfkeywords={regulation, governance, lobbying, regulatory capture, computational simulation, transparency, enforcement}
}

\begin{document}
\maketitle

\section*{Corresponding Author}
Jacob Anderson, Independent Researcher, United States. Email: \texttt{jacobdanderson@gmail.com}

\section*{Target Journal}
Regulation \& Governance. Article type: original article.

\section*{Funding}
No external funding is reported.

\section*{Conflict of Interest}
The author declares no conflicts of interest.

\section*{Data and Code Availability}
\begin{sloppypar}
The simulator source, scenario configurations, validation scripts, generated tables and figures, supporting information files, committed report snapshots, and citation metadata are publicly maintained at \url{https://github.com/Jacoba1100254352/lobby-capture-simulator}. The code is released under the MIT License, and this review bundle is associated with release r208 at \url{https://github.com/Jacoba1100254352/lobby-capture-simulator/releases/tag/paper-publication-readiness-2026-06-19-r208}. Private credentials and raw API payload archives are intentionally excluded from version control.
\end{sloppypar}

\section*{AI Use Disclosure}
OpenAI ChatGPT/Codex was used as an assistant for code scaffolding, editorial revision, research-prompt drafting, and manuscript organization. The author reviewed and edited the output and is responsible for all text, code, citations, analyses, and conclusions. AI tools were not used to fabricate, alter, or manipulate empirical source data or simulation results.

\end{document}
